P.berghei pir analysis

### 2021-09-15 chapter3_results_bergheiPir/Manuscript_Github_Pberghei_pir.Rmd
move stacked_barchart sourcing fun

```{r sourcing_functions}
source('../rfunctions/uniquify_fun.R')
source('../rfunctions/ordering_fun.R')
source('../rfunctions/tpm_fun.R')
source('../rfunctions/usefulFunctions_mround_my-max_firstup_fun.R')
source('../rfunctions/stacked_barchart_fun.R')
```

@@

```{r stacked_barchart}
sd_bars <- TRUE
g_list <- stacked_barchart(melted_tpm = melted_tpm,
                           stack_group_name = 'SorL',
                           sd_bars = sd_bars,
                           inset = TRUE)

>>>>

```{r sourcing_functions}
source('../rfunctions/uniquify_fun.R')
source('../rfunctions/ordering_fun.R')
source('../rfunctions/tpm_fun.R')
source('../rfunctions/usefulFunctions_mround_my-max_firstup_fun.R')
```

@@

```{r stacked_barchart}
source('../rfunctions/stacked_barchart_fun.R')
sd_bars <- TRUE
g_list <- stacked_barchart(melted_tpm = melted_tpm,
                           stack_group_name = 'SorL',
                           sd_bars = sd_bars,
                           inset = TRUE)
